{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Paragraph for higher number of specifications in the outlook

	\paragraph{Larger Range for the Number of Specifications for FPCR}
	\vspace{-0.2cm}

>>>>

	\paragraph{Larger Range for the Number of Specifications for FPCR}
	As alluded to before, the chosen specifications for the number of principal components and the number of basis functions that are used for FPCR might be insufficient to obtain a full picture of the performance of this procedure when combined with smoothing using basis truncation. It would therefore be interesting to focus more attention on this aspect of the paper in a future extension to explore a broader array of possible specifications which might allow the derivation of more detailed insights.
	\vspace{-0.2cm}
